---
title: "Publications"
---

Feel free to contact me if you request a copy or have comments to any work.

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

sapply(c('tibble', 'kableExtra', 'ggplot2'), 
       function(x) library(x, character.only = T))

arts <- tribble(~id, ~ Author, ~Year, ~Title, ~Journal, ~`Vol. ISSUE`, ~doi, ~Coathor, 
        1, 'Ramírez-Mejía, A. F. et al.', 2024, 'How much is enough? Optimizing beehive stocking densities to maximize the production of a pollinator-dependent crop', 'Ecological Modelling', '498', '10.1016/j.ecolmodel.2024.110891', F, 
        1, 'Monasterologo, M, Ramírez-Mejía, A. F., et al.', 2024, 
        'Animal pollination contributes to more than half of Citrus spp. production despite the species and cultivar', 'Scientific reports', 
        '14. 22309', '10.1038/s41598-024-73591-6', T, 
        1, 'Fontanarrosa G., ... Ramírez-Mejía, A. F. ... Piquer-Rodríguez M.', 2024, 
        'Over twenty years of publications in Ecology: Over-contribution of Women reveals a new dimension of gender bias', 'PLOS ONE', NA, '10.1371/journal.pone.0307813', T, 
        1, 'Ramírez-Mejía, A. F. et al.', 2024, "Optimal pollination thresholds to maximize blueberry production", 'Agriculture Ecosystems & Environment', NA, '10.1016/j.agee.2024.108903', F, 
        1, 'Ramírez-Mejía, A. F. et al.', 2023, 'Landscape structure and farming management interacts to modulate pollination supply and crop production in blueberries.', 'Journal of Applied Ecology', 
        NA, '10.1111/1365-2664.14553', F, 
        1, 'Nunes-Silva Patrícia, Ramírez-Mejía, A. F. et al', 2023, 'Book - Blueberry: pollination and production in South America', 'ISBN: 978-65-00-65347-2', NA, '10.5281/zenodo.7770381', T, 
        1, 'Ramírez-Mejía, A. F. et al.', 2023, "Hummingbirds, honeybees, and wild insect pollinators affect yield and berry quality of blueberries depending on cultivar and farm's spatial context", 
        'Agriculture Ecosystems & Environment', NA, '10.1016/j.agee.2022.108229', F, 
        1, 'Blendinger P G, Rojas T. N., Ramírez-Mejía A. F., et al.', 2022, 'Nutrient balance and energy-acquisition effectiveness: do birds adjust their fruit diet to achieve intake targets?', 
        'Functional Ecology', NA, '10.1111/1365-2435.14164', T, 
        1, 'Ramírez-Mejía A. F., et al.', 2022, 'The interplay of spatial scale and landscape transformation moderates the abundance and intraspecific variation in the ecomorphological traits of a phyllostomid bat', 'Journal of Tropical Ecology', NA, '10.1017/S026646742100047X', F, 
        1, 'Ramírez-Mejía A. F., et al.', 2021, 'Activity and habitat use by understory birds in a native Andean forest and a eucalypt plantation', 'Wilson Journal of Ornithology', NA, '10.1676/19-54', F, 
        1, 'Ramírez-Mejía A. F., et al.', 2020, 'Functional diversity of phyllostomid bats in an urban-rural landscape: a scale-dependent analysis', 'Biotropica', NA, '10.1111/btp.12816', F, 
        1, 'Ramírez-Mejía A. F., et al.', 2016, 'Activity patterns and habitat use of mammals in an Andean forest and a Eucalyptus reforestation in Colombia', 'Hystrix, the Italian Journal of Mammalogy', 
        NA, '10.4404/hystrix-27.2-11319', F, 
        1, 'Ramírez-Mejía A. F., et al.', 2015, 'Non-volant mammals in a protected area on the Central Andes of Colombia: new records for the Caldas department and the Chinchiná River basin', 'Check List', 
        NA, '10.15560/11.2.1582', F)

arts$id <- nrow(arts):1


```


```{r, echo=FALSE}
knitr::kable(arts[, -c(6, ncol(arts))], format = 'html', escape = F, 
             caption = 'List of published articles') |> 
  kable_styling(
    font_size = 10,
    bootstrap_options = c('hover', 'condensed', 'responsive'),
    full_width = T
  ) |> 
  row_spec(0, extra_css = "text-align: center") |> 
  column_spec(2, width = '4cm', extra_css = "font-size: 13px; vertical-align: middle;") |> 
  column_spec(6, extra_css = "font-size: 13px; text-align: center; vertical-align: middle;") |> 
  column_spec(c(1, 3, 4, 5), extra_css = "text-align: center; vertical-align: middle;") |> 
  column_spec(1, bold = T)
```


```{r, eval=FALSE, echo=FALSE, fig.width=5, fig.height=1.5, fig.align='center'}

tibble(y = c('First author', 'Coauthorships'), 
       x = c(mean(!arts$Coathor), mean(arts$Coathor))) |> 
  ggplot(aes(x*100, y)) +
  stat_summary(fun = 'max', geom = 'bar', width = 0.2, 
               fill = 'lightblue2') +
  theme_minimal() +
  labs(x = 'Percentage of publications', y = NULL) +
  theme(panel.grid.major.y = element_blank(), 
        text = element_text(family = 'Times New Roman', size =12), 
        panel.grid = element_line(linetype = 3, color = 'tan1'))

```

### Accepted

-   Juliana Wolter ... **Ramírez-Mejía A. F.**..., Rafael Dias. Intrinsic and extrinsic drivers shape frugivore functional diversity within a tree population. *Journal: Ecosphere*. **Role: coauthor, data analysis**

### Articles under review

:::{}
-   **Ramírez-Mejía A. F.**, Mary De Aquino, Michael Castaño Díaz, Juliana Hinz Wolter, Henry S. Pollock, J. Patrick Kelley, Jeferson Vizentin-Bugoni & Corey E. Tarwater. Biotic and abiotic factors directly and indirectly impact the structure of non-trophic networks across a rainfall gradient. *Journal: Ecology*. **Role: first author**

-   Laura Gómez-Murillo, Jeferson Vizentin-Bugoni, **Ramírez-Mejía A. F.**, Corey E. Tarwater. Rainfall alters network structure while fragmentation results in the breakdown of a mixed-species group of birds. *Journal: Oecologia*. **Role: coauthor, data analysis**

-   Elizabeth J. Howard, **Andrés F. Ramírez-Mejía**, Michael Castaño, Mary De Aquino, Henry S. Pollock, Jefferson Vizentin-Bugoni, and Corey E. Tarwater. Testing long standing assumptions about army ant swarms: how profitability and dominance alter space use in birds. **Journal: Behavioral Ecology** .**Role: coauthor, data analysis**

-  Jordan, Kimberley; **Ramírez-Mejía, Andrés F**.; Wilcox, Rebecca C.; Brawn, Jeffrey ; Alfonso, Camilo; Tarwater, Corey. Testing the space-for-time assumption and the hygric niche hypothesis using precipitation effects on avian body condition. **Journal: Proceedings of the Royal Society B: Biological Sciences**. **Role: coauthor, data analysis**

-   **Andrés F. Ramírez-Mejía**, Corey E. Tarwater, J. Patrick Kelley, Jinelle H. Sperry, Jeffrey T. Foster, Donald R. Drake, and Jeferson Vizentin-Bugoni. Temporal dynamics of seed-dispersal networks: Disentangling the role of direct biotic and abiotic factors and bottom-up processes.**Journal: Journal of Animal Ecology**. **Role: first author**

-   Laura Gómez-Murillo, Jeferson Vizentin-Bugoni, **Andrés F. Ramírez-Mejía**, Corey E. Tarwater. Rainfall alters network structure while fragmentation results in the breakdown of a mixed-species group of birds. **Journal: Oecologia**. **Role: coauthor, data analysis**

-  **Andrés F. Ramírez-Mejía**, Francisco Sánchez, J. Nicolás Urbina-Cardona & Natalia Ladino. Functional divergence drives the prevalence of low-abundance species in bat assemblages. **Journal: Functional Ecology**. **Role: first author**


:::

### Manuscript in preparation

:::{}


-   Mauro Galetti,... **Ramírez-Mejía A. F.**... Measuring the macroecological and local effects on plant-animal interaction using artificial fruits. **Role: coauthor, data analysis**

-   **Ramírez-Mejía A. F.**, A. Carolina Monmany, Roxana Aragón, Carolina Cuezzo, Natalia Ladino, Natalí Villalba, A. Carolina Jozami, Alberto Slanis, Mariano Lucia, Leopoldo Alvarez & Natacha P. Chacoff. Low opportunity cost areas in large-scale monoculture for pollinator conservatio. **Role: first author**

-   Mary De Aquino1, Henry S. Pollock, J. Patrick Kelley, **Andrés F. Ramírez-Mejía**, Michael Castaño Díaz1, Jeferson Vizentin-Bugoni  & Corey E. Tarwater. Species’ roles, specialization, and the factors that influence roles in mixed-species animal groups. **Role: review**

:::


### Code and online datasets

:::{}

-   **Ramírez-Mejía A. F.**, Chacoff N., Cavigliasso P., & Blendinger P. (2024). How much is enough? Optimizing beehive stocking densities to maximize the production of a pollinator-dependent crop. *Ecological modelling*, vol 498, article number: <https://doi.org/10.1016/j.ecolmodel.2024.110891>. GitHub repository: <https://github.com/andres-frm/postdoc_cropPol>

-   **Ramírez-Mejía, Andrés F**. (2023). Landscape structure and farming management interacts to modulate pollination supply and crop production in blueberries [code]. **Journal of Applied Ecology**. Zenodo. <https://doi.org/10.5281/zenodo.10070657>

-   **Ramírez-Mejía, Andrés F**. et al. (2023). Landscape structure and farming management interacts to modulate pollination supply and crop production in blueberries [Dataset]. **Journal of Applied Ecology**. Dryad. <https://doi.org/10.5061/dryad.bg79cnphc>

-   **Ramírez-Mejía, A F**.; Urbina-Cardona, J N; Sánchez, F (2020). Data from: Functional diversity of phyllostomid bats in an urban-rural landscape: a scale-dependent analysis [Dataset]. **Biotropica**. Dryad. <https://doi.org/10.5061/dryad.sn02v6x1p>
:::


### Technical guides

-   Federico Fritz ... **Ramírez-Mejía, Andrés F**, et al. 2025. Gestión de la biodiversidad en los agroecosistemas. 1a ed. - Ciudad Autónoma de Buenos Aires : Asociación Argentina de Consorcios Regionales de Experimentación Agrícola - AACREA, 2025. 120 p. ; 26 x 20 cm. ISBN 978-987-1513-33-8

### Theses

:::{}
-   **PhD degree** --- (2018 - 2023). The step-by-step of pollination service in blueberry crops: patterns and mechanisms. Thesis advisors: [Dr Pedro G. Blendinger](https://scholar.google.com/citations?user=9oyNtX0AAAAJ&hl=en&oi=ao); independent research CONICET, assistant professor UNT. [Dr Silvia Lomáscolo](https://scholar.google.com/citations?hl=en&user=r9PAo-QAAAAJ); assistant researcher CONICET.

-   **Master's degree** --- (2015 - 2017) Seed dispersion and functional diversity of phyllostomid bats in an anthropogenic landscape: a multi-scale approach. Thesis advisors: [Dr Francisco Sánchez](https://scholar.google.com/citations?user=6MC0Yx8AAAAJ&hl=en); Universidad de los Llanos, Colombia. [Dr J. Nicolás Urbina-Cardona](https://scholar.google.com/citations?user=uMBjaFgAAAAJ&hl=en); Pontificia Universidad Javeriana, Colombia.

-   **Undergraduate** --- (2008 - 2014) Activity, habitat use and richness of mammals in native forest and eucalyptus reforestations in the Colombian Andes. Thesis advisor: [Dr Francisco Sánchez](https://scholar.google.com/citations?user=6MC0Yx8AAAAJ&hl=es); Universidad Militar Nueva Granada, Cundinamarca, Colombia.
:::
